\vspace{1.0cm} \LARGE \bf Supporting Text: \\ Integrating influenza antigenic dynamics with molecular evolution

### 2013-02-22 cover_letter.tex
Revise cover letter.

Since the publication of ``Mapping the Antigenic and Genetic Evolution of Influenza Virus'' by Smith et al. in 2004, there has been significant interest in characterizing patterns of antigenic and genetic evolution in seasonal influenza.
Such cartographic approaches use multidimensional scaling (MDS) to position viruses and antisera on an antigenic map so that distances between viruses and antisera predict observed serological data.
Here, we present a substantial advance to previous approaches that uses Bayesian multidimensional scaling (BMDS) to place antigenic cartography in a fully probabilistic framework.
Doing so has allowed us to build in important covariates into the antigenic model; most importantly, phylogenetic relationships.
Thus, our method simultaneously models evolutionary and antigenic dynamics, and allows us to infer which phylogeny branches have evolved in antigenic phenotype and which branches have remained static.

@@

Both the link between incidence and antigenic drift and the presence of interference across influenza subtypes have remained large-standing questions in the influenza community.
We believe our results do much to address these questions.
Additionally, we believe our methodological advances will prove fundamental to future research in influenza and other antigenically variable pathogens.
Our unified genetic / antigenic approach makes it possible to look closely for causal relationships between genetic mutations and antigenic change, and to characterize, for the first time, the antigenic mutations that are ultimately successful in the global competition among virus lineages.

>>>>

Since the publication of ``Mapping the Antigenic and Genetic Evolution of Influenza Virus'' by Smith et al. in 2004, there has been significant interest in assessing patterns of antigenic and genetic evolution in seasonal influenza.
Such cartographic approaches use multidimensional scaling (MDS) to position viruses and antisera on an antigenic map so that distances between viruses and antisera predict observed serological data.
Here, we present a substantial advance to previous approaches that uses Bayesian multidimensional scaling (BMDS) to place antigenic cartography in a fully probabilistic framework.
Doing so has allowed us to build in important covariates into the statistical model; most importantly, phylogenetic relationships.
Thus, our method simultaneously models evolutionary and antigenic dynamics, and allows us to infer which phylogeny branches have evolved in antigenic phenotype and which branches have remained static.

@@

Both the link between incidence and antigenic drift and the presence of interference across influenza subtypes have remained long-standing questions in the influenza community.
We believe our results do much to address these questions.
Additionally, we believe our methodological advances will prove fundamental to future research in influenza and other antigenically variable pathogens.
Our unified genetic / antigenic approach will make it possible to look closely for causal relationships between genetic mutations and antigenic change, and to characterize, for the first time, the antigenic mutations that are ultimately successful in the global competition among virus lineages.
